%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{Aaron Creor}
\address{github.com/AaronCreor \linebreak linkedin.com/in/aaroncreor \linebreak aaroncreor.com}
\contacts{(604) 217-2514 \linebreak aaron@aaroncreor.com}
\begin{document}

	% Print the header
	\makeheader
	
	% Print the content
	\begin{cvsection}{Employment}
		\begin{cvsubsection}{Programmer 2}{Jim Pattison Food Group}{December 2023 - Present}		
			\begin{itemize}
				\item Acted as an SME for integrating modernized supply chain infrastructure with legacy systems using \textbf{IICS}.
				\item Utilized extensive scripting in\textbf{Bash} to automate assignment of tax groups to new items.
				\item Streamlined the SDLC for developers by implementing an updated \textbf{CI/CD} system with GitHub Actions.
				\item Mentored and trained junior programmers, instilling best practices and positive habits.
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Programmer 1}{Jim Pattison Food Group}{May 2022 -- December 2023}	
			\begin{itemize}
				\item Developed \textbf{SOAP} services to automate common fixes, significantly reducing time spent on recurring issues.
				\item Designed and implemented legal agreement pages leveraging \textbf{JavaScript} and \textbf{.NET}, while capturing user responses.
				\item Addressed regular production bugs and improvements in existing Java services using \textbf{Jira} to prioritize requirements.
				\item Upgraded security libraries for legacy \textbf{C\#} applications to streamline password reset processes, transitioning from direct \textbf{LDAP} integration to \textbf{AD}.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Education}
		\begin{cvsubsection}{M.S. Computer Science}{University of Texas at Austin}{Fall 2024 -- Spring 2027}
			\begin{itemize}
				\item Graduate Coursework: Machine Learning, Mobile Development, Deep Learning, Advanced Linear Algebra.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{B.S. Computer Science}{University of the Fraser Valley}{Fall 2017 -- Spring 2022}
			\begin{itemize}
				\item Undergraduate Coursework: Operating Systems, Databases, Algorithms, Data Structures, Networks.
				\item UFV Student Computing Association Vice President (2021 – 2022)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Projects}
		\begin{cvsubsection}{Stock Market Showdown}{}{}
		\texttt{github.com/AaronCreor/StockMarketShowdown}
			\begin{itemize}
				\item Developed a stock market simulation game in \textbf{Kotlin}, allowing users to buy and sell stocks in real-time.
				\item Leveraged \textbf{MySQL} database hosted in \textbf{AWS}, with a robust schema to manage user data, transactions, and portfolios.
				\item Utilized various third-party APIs such as Finnhub to acquire real-time market updates.
				\item Integrated real-time stock market data visualization using the \textbf{Charts.kt} library.
				\item Implemented user authentication and management with \textbf{Firebase}, enabling secure login, registration, and session management.
			\end{itemize}
		\end{cvsubsection}
		\begin{cvsubsection}{CFIA Compliance Project}{}{}
			\begin{itemize}
				\item Led enhancement of existing Jim Pattison Food Group proprietary systems to come into compliance with new CFIA (Canada Food Inspection Agency) regulations.
				\item Implemented changes across multiple systems including a \textbf{C\#} web frontend, \textbf{Java} application server backend, and a \textbf{PL/SQL} DB.
				\item Collaborated closely with stakeholders to gather, define, and prioritize functional and technical requirements.
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Languages and Technologies}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Languages: Java, Kotlin, Python, JavaScript/HTML/CSS, C\# (ASP.NET), SQL, Bash, YAML
				\item Tools: Git, SVN, Linux, Gradle, Maven, Jira, CI/CD, Powershell
				\item Cloud: AWS (RDS), Azure (AD, Exchange, DB), Firebase (Firestore, Auth, Realtime Database)
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}

